ShabbyPages: A Reproducible Document Denoising and Binarization Dataset

### 2023-02-11 paper/paper.tex
Updated spellings

\begin{table}[]
    \centering
    \caption{Summary of datasets for document binarization (above line) and document denoising (below line) tasks. Datasets listed below the line contain synthetic noise.}
    \label{tab:datasets}
    \begin{tabular}{lclllllll}
        \textbf{Dataset} &
        \rot{80}{\textbf{Dataset Size}}
            & \rot{80}{\textbf{Synthetic Noise}}
            & \rot{80}{\textbf{Ground-Truths}}
            %& \rot{80}{\textbf{Diversity}}
            & \rot{80}{\textbf{Varied fonts/sizes}}
            & \rot{80}{\textbf{Varied paper styles}}
            & \rot{80}{\textbf{Multilingual}}
            & \rot{80}{\textbf{Contains graphics}}
            & \rot{80}{\textbf{Reproducible}}\\
            \midrule
         \emph{DIBCO-9} \cite{dibco-09} & 10 & \xmark & \cmark &   \cmark & \cmark & \cmark & \xmark & n/a \\
         \emph{DIBCO-10} \cite{dibco-10} & 10 & \xmark & \cmark &  \cmark & \cmark & \xmark & \xmark & n/a \\
         \emph{DIBCO-11} \cite{dibco-11} & 16 & \xmark & \cmark &  \cmark & \cmark & \cmark & \xmark & n/a\\
         \emph{DIBCO-12} \cite{dibco-12} & 14 & \xmark & \cmark &  \cmark & \cmark & \xmark & \xmark & n/a \\
         \emph{DIBCO-13} \cite{dibco-13} & 16 & \xmark & \cmark &  \cmark & \cmark & \cmark & \xmark & n/a \\
         \emph{H-DIBCO-14} \cite{dibco-14} & 10 & \xmark & \cmark & \cmark & \cmark & \cmark & \xmark & n/a \\
         \emph{H-DIBCO-16} \cite{dibco-16} & 10 & \xmark & \cmark & \cmark & \cmark & \cmark & \xmark & n/a \\
         \emph{DIBCO-17} \cite{dibco-17} & 20 & \xmark & \cmark & \cmark & \cmark & \cmark & \xmark & n/a \\
         \emph{H-DIBCO-18} \cite{dibco-18} & 10 & \xmark & \cmark  & \cmark & \cmark & \cmark & \xmark & n/a\\
         %\emph{DIBCO-19} \cite{dibco-19} & & \xmark & & & & & & & n/a\\ % SL: I can't find this dataset online
         \emph{Bickley Diary} \cite{bickley-diary} & 7 & \xmark & \cmark   & \xmark & \xmark & \xmark & \xmark & n/a\\
         \emph{PHIBD} \cite{nafchi-2013-icdar} & 15 & \xmark & \cmark &   \cmark & \cmark & \xmark & \xmark & n/a\\
         %TQBC & & & & & & & & & n/a\\ % SL: I can't find this dataset online
         \midrule
         \emph{NoisyOffice} \cite{ref_NoisyOffice} & 72  & \cmark & \cmark &  \cmark & \xmark & \xmark & \xmark & \xmark \\ % div: 0.317
         \emph{DocCreator} \cite{ref_DocCreator} & 6,059 & \cmark & \cmark & \cmark & \cmark & \cmark & \xmark &\cmark\\
         %LS-HDIB \cite{ls-hdib-2021} & & \cmark & & & & & & & \\
         \emph{DDI-100} \cite{ddi-100-2019} & 100k+~ & \cmark & \cmark & \cmark & \xmark & \xmark & \cmark & \xmark\\
         \emph{ShabbyPages} (ours)~ & 6,202~ & \cmark & \cmark  & \cmark~ & \cmark~ & \cmark & \cmark & \cmark \\ % div: 0.488
         \bottomrule
    \end{tabular}
\end{table}

@@

\begin{figure}
    \centering\scalebox{0.365}{
    \includegraphics{figures/ddi-100-samples-1.pdf}}
    \caption{Example noisy-clean pairs from DDI-100. Geometric transformations are required to map the noisy samples to their corresponding clean ground-truth images, making DDI-100 unsuitable for binarization and denoising.}
    \label{fig:ddi-100-samples}
\end{figure}

@@

Other popular document image datasets --- like RVL-CDIP \cite{ref_RVL-CDIP}, Tobacco-3482 [CITE], Tobacco-800 \cite{ref_Tobacco800}, and FUNSD [cite] --- include large amounts of real noise, but none of these have corresponding clean ground-truth document images to train or evaluate document denoisers and binarizers.

@@

\subsubsection{Developing the Pipeline.}
The \emph{Augraphy} library presents an easy-to-use API for constructing data augmentation pipelines for document images, which has been designed for interoperability with other augmentation tools, and within the broader data ecosystem.
While \emph{Augraphy}'s default pipeline has what we believe to be quite realistic defaults, we wanted a broader range of features from this dataset than those the default pipeline could produce.
To address this, we broke all of the parameters for every augmentation constructor out into separate variables, tweaking these and committing the new pipeline to GitHub.
We created an automated daily build in GitHub Actions to render a random selection of ground-truth images with the updated pipeline, then our team met frequently to discuss the output and make adjustments to the augmentation parameters, until we were consistently satisfied with the results.

@@

Several challenges arose in the construction of this dataset.
Old fax machines, faulty commercial printers, and other hardware suitable for inducing the intended effects were difficult to source, and frequently non-functional when they could be found.
Environmental concerns like the volume of paper and ink used, and the energy expenditure both in electricity and human terms, also factored into our decision to pursue synthetic augmentations for \emph{ShabbyPages}.
Manually producing a database of noisy documents is a time-consuming and repetitive task; creating just 200 real-world documents with real noise features required the labor of several people.
Nevertheless, despite the limited size of the resulting dataset, the scarcity of real-world datasets with ground truth images makes the \emph{ShabbyReal} corpus extremely valuable; its inclusion in \emph{ShabbyPages} even moreso.
This type of dataset is critical for benchmark comparison with synthetically-augmented document images, and for other tasks such as denoising and binarizing: we use \emph{ShabbyReal} later for a human-perception evaluation of denoising performance.

@@

\section{Experimentation with the \emph{ShabbyPages} Set}
Denoising and binarization are two important techniques for the removal of unwanted data from images.
Both approaches can be achieved by supervised learning of relationships between features of the input and output data.
In this section, we train two NAFNet \cite{ref_nafnet} instances as denoisers on both the \mbox{\emph{NoisyOffice}} and the \mbox{\emph{ShabbyPages}} datasets. We evaluate these models' predictions in a cross-validation test on both datasets, both by visual inspection and by metric computation.
We then perform a similar experiment where the same NAFNets are trained to not only remove noise from the test images, but also to classify the foreground and backgorund pixels, predicting a binarized clean document.
The model was ``off-the-shelf''; besides rigging up the training inputs and choosing a reasonable training epoch limit, we made no significant alterations to the provided hyperparameters.

\subsection{Denoising}
Digital computation has enabled humanity to produce ever-growing amounts of both data and reasons to process it.
Doing so is easiest when the data is free of unexpected outliers, the signal has less jitter, and perhaps most importantly, when our aesthetic sensibilities are un-challenged.

>>>>

\begin{table}[]
    \centering
    \caption{Summary of datasets for document binarization (above line) and document denoising (below line) tasks. Datasets listed below the line contain synthetic noise.}
    \label{tab:datasets}
    \begin{tabular}{lclllllll}
        \textbf{Dataset} &
        \rot{80}{\textbf{Dataset Size}}
            & \rot{80}{\textbf{Synthetic Noise}}
            & \rot{80}{\textbf{Groundtruths}}
            %& \rot{80}{\textbf{Diversity}}
            & \rot{80}{\textbf{Varied fonts/sizes}}
            & \rot{80}{\textbf{Varied paper styles}}
            & \rot{80}{\textbf{Multilingual}}
            & \rot{80}{\textbf{Contains graphics}}
            & \rot{80}{\textbf{Reproducible}}\\
            \midrule
         \emph{DIBCO-9} \cite{dibco-09} & 10 & \xmark & \cmark &   \cmark & \cmark & \cmark & \xmark & n/a \\
         \emph{DIBCO-10} \cite{dibco-10} & 10 & \xmark & \cmark &  \cmark & \cmark & \xmark & \xmark & n/a \\
         \emph{DIBCO-11} \cite{dibco-11} & 16 & \xmark & \cmark &  \cmark & \cmark & \cmark & \xmark & n/a\\
         \emph{DIBCO-12} \cite{dibco-12} & 14 & \xmark & \cmark &  \cmark & \cmark & \xmark & \xmark & n/a \\
         \emph{DIBCO-13} \cite{dibco-13} & 16 & \xmark & \cmark &  \cmark & \cmark & \cmark & \xmark & n/a \\
         \emph{H-DIBCO-14} \cite{dibco-14} & 10 & \xmark & \cmark & \cmark & \cmark & \cmark & \xmark & n/a \\
         \emph{H-DIBCO-16} \cite{dibco-16} & 10 & \xmark & \cmark & \cmark & \cmark & \cmark & \xmark & n/a \\
         \emph{DIBCO-17} \cite{dibco-17} & 20 & \xmark & \cmark & \cmark & \cmark & \cmark & \xmark & n/a \\
         \emph{H-DIBCO-18} \cite{dibco-18} & 10 & \xmark & \cmark  & \cmark & \cmark & \cmark & \xmark & n/a\\
         %\emph{DIBCO-19} \cite{dibco-19} & & \xmark & & & & & & & n/a\\ % SL: I can't find this dataset online
         \emph{Bickley Diary} \cite{bickley-diary} & 7 & \xmark & \cmark   & \xmark & \xmark & \xmark & \xmark & n/a\\
         \emph{PHIBD} \cite{nafchi-2013-icdar} & 15 & \xmark & \cmark &   \cmark & \cmark & \xmark & \xmark & n/a\\
         %TQBC & & & & & & & & & n/a\\ % SL: I can't find this dataset online
         \midrule
         \emph{NoisyOffice} \cite{ref_NoisyOffice} & 72  & \cmark & \cmark &  \cmark & \xmark & \xmark & \xmark & \xmark \\ % div: 0.317
         \emph{DocCreator} \cite{ref_DocCreator} & 6,059 & \cmark & \cmark & \cmark & \cmark & \cmark & \xmark &\cmark\\
         %LS-HDIB \cite{ls-hdib-2021} & & \cmark & & & & & & & \\
         \emph{DDI-100} \cite{ddi-100-2019} & 100k+~ & \cmark & \cmark & \cmark & \xmark & \xmark & \cmark & \xmark\\
         \emph{ShabbyPages} (ours)~ & 6,202~ & \cmark & \cmark  & \cmark~ & \cmark~ & \cmark & \cmark & \cmark \\ % div: 0.488
         \bottomrule
    \end{tabular}
\end{table}

@@

\begin{figure}
    \centering\scalebox{0.365}{
    \includegraphics{figures/ddi-100-samples-1.pdf}}
    \caption{Example noisy-clean pairs from DDI-100. Geometric transformations are required to map the noisy samples to their corresponding clean groundtruth images, making DDI-100 unsuitable for binarization and denoising.}
    \label{fig:ddi-100-samples}
\end{figure}

@@

Other popular document image datasets --- like RVL-CDIP \cite{ref_RVL-CDIP}, Tobacco-3482 [CITE], Tobacco-800 \cite{ref_Tobacco800}, and FUNSD [cite] --- include large amounts of real noise, but none of these have corresponding clean groundtruth document images to train or evaluate document denoisers and binarizers.

@@

\subsubsection{Developing the Pipeline.}
The \emph{Augraphy} library presents an easy-to-use API for constructing data augmentation pipelines for document images, which has been designed for interoperability with other augmentation tools, and within the broader data ecosystem.
While \emph{Augraphy}'s default pipeline has what we believe to be quite realistic defaults, we wanted a broader range of features from this dataset than those the default pipeline could produce.
To address this, we broke all of the parameters for every augmentation constructor out into separate variables, tweaking these and committing the new pipeline to GitHub.
We created an automated daily build in GitHub Actions to render a random selection of groundtruth images with the updated pipeline, then our team met frequently to discuss the output and make adjustments to the augmentation parameters, until we were consistently satisfied with the results.

@@

Several challenges arose in the construction of this dataset.
Old fax machines, faulty commercial printers, and other hardware suitable for inducing the intended effects were difficult to source, and frequently non-functional when they could be found.
Environmental concerns like the volume of paper and ink used, and the energy expenditure both in electricity and human terms, also factored into our decision to pursue synthetic augmentations for \emph{ShabbyPages}.
Manually producing a database of noisy documents is a time-consuming and repetitive task; creating just 200 real-world documents with real noise features required the labor of several people.
Nevertheless, despite the limited size of the resulting dataset, the scarcity of real-world datasets with ground truth images makes the \emph{ShabbyReal} corpus extremely valuable; its inclusion in \emph{ShabbyPages} even more so.
This type of dataset is critical for benchmark comparison with synthetically-augmented document images, and for other tasks such as denoising and binarizing: we use \emph{ShabbyReal} later for a human-perception evaluation of denoising performance.

@@

\section{Experimentation with the \emph{ShabbyPages} Set}
Denoising and binarization are two important techniques for the removal of unwanted data from images.
Both approaches can be achieved by supervised learning of relationships between features of the input and output data.
In this section, we train two NAFNet \cite{ref_nafnet} instances as denoisers on both the \mbox{\emph{NoisyOffice}} and the \mbox{\emph{ShabbyPages}} datasets. We evaluate these models' predictions in a cross-validation test on both datasets, both by visual inspection and by metric computation.
We then perform a similar experiment where the same NAFNets are trained to not only remove noise from the test images, but also to classify the foreground and background pixels, predicting a binarized clean document.
The model was ``off-the-shelf''; besides rigging up the training inputs and choosing a reasonable training epoch limit, we made no significant alterations to the provided hyperparameters.

\subsection{Denoising}
Digital computation has enabled humanity to produce ever-growing amounts of both data and reasons to process it.
Doing so is easiest when the data is free of unexpected outliers, the signal has less jitter, and perhaps most importantly, when our aesthetic sensibilities are unchallenged.
